Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-02-13 inst/examples/20170201-manuscript.Rmd
manuscript figures

```{r places_per_decade, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
              group_by(catalog, publication_decade) %>%
	      summarise(n = length(unique(na.omit(publication_place))))
p <- ggplot(df, aes(x = publication_decade, y = n, shape = catalog, linetype = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Places (n)") + xlab("Publication year") +
       scale_color_manual(values = c("blue", "darkgreen")) + 
       guides(color = guide_legend(reverse = TRUE, title = "")) +
       ggtitle("Unique publication places")
print(p)
```

@@

```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>% group_by(catalog, publication_decade) %>% tally()
p <- ggplot(df, aes(x = publication_decade, y = n, shape = catalog, linetype = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Documents (n)") + xlab("Publication year") +
       scale_color_manual(values = c("blue", "darkgreen")) + 
       guides(color = guide_legend(reverse = TRUE, title = "")) +
       ggtitle("Title count")
print(p)
```

@@

```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=11, fig.height=9, fig.show="hold", out.width="350px"}
for (catal in unique(df0$catalog)) {
  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper = sum(paper, na.rm = TRUE), n = n()) 
  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
  df2$highlight <- rep("Other", nrow(df2))
  df2$highlight[df2$gatherings == "8vo"] <- "Octavo"

  p <- ggplot(df2, aes(y = paper,
                       x = publication_decade,
  	       shape = gatherings,
		       linetype = gatherings))		       
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1,
         aes(color = highlight, fill = highlight))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
  p <- p + ggtitle("Paper consumption in time by gatherings")
  p <- p + xlab("Year")
  p <- p + ylab("Paper consumption")
  p <- p + guides(linetype = guide_legend(keywidth = 5, title = "Gatherings"),
       	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
       	          fill = "none" 
		  )
  p <- p + ggtitle(catal)
  print(p)
}
```

@@

p <- ggplot(df, aes(x = publication_decade, y = mean_title_length,
                     fill = language)) +
       geom_point(aes(size = n, shape = language), size = 3) +
       geom_line(aes(linetype = language), size = 1) +
       guides(
            shape = guide_legend(title = "Language")
	    ) +
       ylab("Title length (word count)") +
       xlab("Publication decade") +
       ggtitle("Title length")

@@

p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
       geom_line(aes(linetype = publication_place), size = 1) +
       geom_point(aes(shape = publication_place), size = 5) +
       xlab("Publication decade") +
       ylab("Title count per capita (n)") +
       ggtitle("Title count per capita") +
       guides(shape = guide_legend(title = "Place"))
print(p)

@@

p <- ggplot(df, aes(x = publication_decade, y = paper)) +
       geom_line(aes(linetype = publication_place), size = 1) +
       geom_point(aes(shape = publication_place), size = 5) +
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       ggtitle("Octavo: paper consumption") +
       guides(shape = guide_legend(shape = "Place"))
print(p)
```

@@

p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_line(aes(linetype = publication_place), size = 1) +
       geom_point(aes(shape = publication_place), size = 5) +
       xlab("Publication year") +
       ylab("Title length (characters)") +
       ggtitle("Mean title length in selected cities") +
       guides(shape = guide_legend(title = "Place"))
print(p)
```

@@

  for (myplace in myplaces) {
    p <- ggplot(subset(dff, publication_place == myplace),
      aes(x = publication_decade, y = f)) +
      geom_bar(position = "stack", stat = "identity",
      			aes(fill = language), color = "black") + 
      xlab("Publication year") +
      ylab("Title count frequency (%)") +
      ggtitle(paste(myplace, "/", catalogue)) +
      #scale_fill_brewer(palette="Spectral") +
      scale_fill_brewer(palette="Greys") +       
      guides(fill = guide_legend(title = ""))
    pics[[paste(catalogue, myplace, sep = "-")]] <- p
  }
}

@@

p <- ggplot(df, aes(x = publication_year, y = n, shape = language)) +
       geom_line(size = 1, aes(linetype = language)) +
       geom_point(size = 4) +
       scale_color_brewer(palette="Greys") +
       scale_fill_brewer(palette="Greys") +                     
       geom_smooth(color = "black") +       
       ylab("Title count (n)") + xlab("Publication year")

@@

  # PAPER CONSUMPTION
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language), size = 5) +
       geom_line(aes(linetype = language), size = 1) +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       ggtitle(paste("Temporary Sermons (", catalogue, ")", sep = ""))
  print(p)
```

@@

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language), size = 5) +
       geom_line(aes(linetype = language)) +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       guides(shape = guide_legend(title = "Language")) +
       ggtitle(paste("Devotional Literature (", catalogue, ")", sep = ""))
  print(p)
```

>>>>

```{r places_per_decade, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>%
              group_by(catalog, publication_decade) %>%
	      summarise(n = length(unique(na.omit(publication_place))))
p <- ggplot(df, aes(x = publication_decade, y = n, shape = catalog, linetype = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Places (n)") + xlab("Publication year") +
       scale_color_manual(values = c("blue", "darkgreen")) + 
       guides(color = guide_legend(title = "")) +
       ggtitle("Unique publication places")
print(p)
```

@@

```{r, message=FALSE, warning=FALSE, fig.width=10, fig.height=4, echo=FALSE}
library(dplyr)
library(ggplot2)
theme_set(theme_bw(20))
df <- df0 %>% filter(publication_year >=1640 & publication_year <=1828) %>% group_by(catalog, publication_decade) %>% tally()
p <- ggplot(df, aes(x = publication_decade, y = n, shape = catalog, linetype = catalog)) + 
       geom_point(size = 4) + 
       geom_line(size = 1) + 
       ylab("Documents (n)") + xlab("Publication year") +
       scale_color_manual(values = c("blue", "darkgreen")) + 
       guides(color = guide_legend(title = "")) +
       ggtitle("Title count")
print(p)
```

@@

```{r LIBER-13, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE, fig.width=6, fig.height=5, fig.show="hold", out.width="400px"}
for (catal in unique(df0$catalog)) {
  df2 <- subset(df0, catalog == catal) %>% group_by(publication_decade, gatherings) %>% summarize(paper = sum(paper, na.rm = TRUE), n = n()) 
  df2 <- filter(df2, gatherings %in% setdiff(names(which(table(df2$gatherings) >= 15)), "NA"))
  df2$highlight <- rep("Other", nrow(df2))
  df2$highlight[df2$gatherings == "8vo"] <- "Octavo"

  p <- ggplot(df2, aes(y = paper,
                       x = publication_decade,
  	       shape = gatherings,
		       linetype = gatherings))		       
  p <- p + geom_point(size = 4)
  p <- p + geom_smooth(method = "loess", size = 1,
         aes(color = highlight, fill = highlight))
  p <- p + scale_color_manual(values = c("darkgreen", "darkgray"))
  p <- p + scale_fill_manual(values = c("darkgreen", "darkgray"))  	 
  p <- p + ggtitle("Paper consumption in time by gatherings")
  p <- p + xlab("Year")
  p <- p + ylab("Paper consumption")
  p <- p + guides(linetype = guide_legend(keywidth = 5, title = "Gatherings"),
       	          shape = guide_legend(keywidth = 5, title = "Gatherings"),
       	          fill = guide_legend(title = "Gatherings")
		  )
  p <- p + ggtitle(catal)
  print(p)
}
```

@@

p <- ggplot(df, aes(x = publication_decade, y = mean_title_length,
                     fill = language)) +
       geom_point(aes(size = n, shape = language), size = 3) +
       geom_line(aes(linetype = language), size = 1) +
       guides(
            shape = guide_legend(title = "Language"),
            linetype = guide_legend(title = "Language")
	    ) +
       ylab("Title length (word count)") +
       xlab("Publication decade") +
       ggtitle("Title length")

@@

p <- ggplot(dfm, aes(x = publication_decade, y = titles_per_capita)) +
       geom_line(aes(linetype = publication_place), size = 1) +
       geom_point(aes(shape = publication_place), size = 5) +
       xlab("Publication decade") +
       ylab("Title count per capita (n)") +
       ggtitle("Title count per capita") +
       guides(shape = guide_legend(title = "Place")) +
       guides(linetype = guide_legend(title = "Place")) 
print(p)

@@

p <- ggplot(df, aes(x = publication_decade, y = paper)) +
       geom_line(aes(linetype = publication_place), size = 1) +
       geom_point(aes(shape = publication_place), size = 5) +
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       ggtitle("Octavo: paper consumption") +
       guides(shape = guide_legend(title = "Place")) +
       guides(linetype = guide_legend(title = "Place"))        
print(p)
```

@@

p <- ggplot(df, aes(x = publication_decade, y = mean_title_length)) +
       geom_line(aes(linetype = publication_place), size = 1) +
       geom_point(aes(shape = publication_place), size = 5) +
       xlab("Publication year") +
       ylab("Title length (characters)") +
       ggtitle("Mean title length") +
       guides(shape = guide_legend(title = "Place")) +
       guides(linetype= guide_legend(title = "Place"))        
print(p)
```

@@

  for (myplace in myplaces) {
    p <- ggplot(subset(dff, publication_place == myplace),
      aes(x = publication_decade, y = f)) +
      geom_bar(position = "stack", stat = "identity",
      			aes(fill = language), color = "black") + 
      xlab("Publication year") +
      ylab("Title count frequency (%)") +
      ggtitle(paste(myplace, "/", catalogue)) +
      #scale_fill_brewer(palette="Spectral") +
      scale_fill_brewer(palette="Greys") +       
      guides(fill = guide_legend(title = "")) 
      #guides(fill = guide_legend(title = "")) +       
    pics[[paste(catalogue, myplace, sep = "-")]] <- p
  }
}

@@

p <- ggplot(df, aes(x = publication_year, y = n, shape = language)) +
       geom_line(size = 1, aes(linetype = language)) +
       geom_point(size = 4) +
       scale_color_brewer(palette="Greys") +
       scale_fill_brewer(palette="Greys") +                     
       geom_smooth(color = "black") +
       guides(shape = guide_legend(title = "Language")) +
       guides(linetype = guide_legend(title = "Language")) + 
       ylab("Title count (n)") + xlab("Publication year")

@@

  # PAPER CONSUMPTION
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language), size = 5) +
       geom_line(aes(linetype = language), size = 1) +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       guides(shape = guide_legend(title = "Language")) +
       guides(linetype = guide_legend(title = "Language")) + 
       ggtitle(paste("Temporary Sermons (", catalogue, ")", sep = ""))
  print(p)
```

@@

  # PAPER CONSUMPTION
  theme_set(theme_bw(20))
  p <- ggplot(df, aes(x = publication_decade, y = paper, group = language)) +
       geom_point(aes(shape = language), size = 5) +
       geom_line(aes(linetype = language)) +       
       xlab("Publication year") +
       ylab("Paper consumption") +
       guides(shape = guide_legend(title = "Language")) +
       guides(linetype = guide_legend(title = "Language")) +        
       ggtitle(paste("Devotional Literature (", catalogue, ")", sep = ""))
  print(p)
```
